---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# SeabirdStudio

An R package for exploring and comparing seabird colony/site community composition.

## Installation

You can install SeabirdStudio from [GitHub](https://github.com/) with:


# install.packages("pak")
pak::pak("StineGryt/SeabirdStudio")


## Included data

The package includes a subset of seabird colony count data from the UK. 

```{r}
library(SeabirdStudio)
data("seabird_counts")
head(seabird_counts)
```


## Functions

### List available sites

```{r}
list_colonies(seabird_counts)
```


### Species richness

```{r}
species_richness(seabird_counts, "Foula")
```


### Relative abundance

```{r}
relative_abundance(seabird_counts, "Ailsa Craig")
```


### Colony similarity (Bray-Curtis similarity index)

```{r}
colony_similarity(seabird_counts, "Lambay", "Foula")
```


## Shiny app
Launch the interactive app:

run_seabird_app()

## Description

This package provides simple tools for exploring seabird community composition and comparing colonies/seabird sites using ecological metrics.

## Data source

The dataset included in this package is a curated subset of seabird colony data from the Joint Nature Conservation Committee (JNCC) Seabirds Count programme.

Source:
https://jncc.gov.uk/our-work/seabirds-count/

